Fast, Scalable Phrase-Based SMT Decoding

### 2016-03-03 acl.2016/acl2016.tex
Minor clarity

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm~\cite{Chiang:2007:cl} with a pop-limit of 400, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employ by users who require fast decoding as it gives them the ability to trade speed with translation quality with a simple pop-limit parameter.

>>>>

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm~\cite{Chiang:2007:cl} with a pop-limit of 400, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employed by users who require fast decoding as it gives them the ability to trade speed with translation quality via a simple pop-limit parameter.
